HEP Software Foundation Community White Paper Working Group -- Training, Staffing and Careers

### 2018-06-13 CWP/papers/HSF-CWP-2017-02_training/latex/cwp-wg-training-careers.tex
Tutorial of the month.

The adoption of such an approach is made rather easy in WikiToLearn by the
relative simplicity of the wikimedia-based toolset: users contribute their
training material using just a web-browser, and in order to do this efficiently,
the necessary learning curve has been kept appropriately shallow.
An interesting exercise in this context has recently been made by colleagues of
the GridKa School of computing: the material from this year (2017) has been made
publicly available on WTL~\cite{WikiToLearnGridka}.
This constitutes an intersting example of what can be accomplished using this
the necessary learning curve has been kept appropriately shallow. An interesting exercise in
this context has recently been made by colleagues of
the GridKa School of computing: the material from this year (2017) has been made
publicly available on WTL\footnote{\url{https://en.wikitolearn.org/GridKa2017}}.
This constitutes an interesting example of what can be accomplished using this
platform; it is just a first example of what's possible, but an inspiring one.

Another example of web-based platform is a collection of online tutorials
(mostly written in french) hosted on the Gitlab IN2P3
server{\url{https://gitlab.in2p3.fr/MaitresNageurs}}. Taking profit of
the Gitlab ability to host Docker images, those tutorials aims to avoid the
"damned installation step" that often absorbs half of a training session.
Similarly to the GridKa School for WikiToLearn, the annual IN2P3 Computing
Days are an opportunity to refresh and extend the collection of
tutorials every year. Future work will focus on english translation, and the
development of a web site which will index the above tutorials, together with
the best recommended external tutorials.

@@

>>>>

The adoption of such an approach is made rather easy in WikiToLearn by the
relative simplicity of the wikimedia-based toolset: users contribute their
training material using just a web-browser, and in order to do this efficiently,
the necessary learning curve has been kept appropriately shallow.

An interesting exercise in this context has recently been made by colleagues of
the GridKa School of computing: the material from this year (2017) has been made
publicly available on WTL~\cite{WikiToLearnGridka}.
This constitutes an intersting example of what can be accomplished using this
platform; it is just a first example of what's possible, but an inspiring one.

@@

In the context of web-based training, if HSF helps to constitute a living
collection of online tutorials, we could organize regular events such as
a "Tutorial of the month", based on students votes. From a more general point
of view, since the publications are the most universal recognized items
in the research community, we should try hardly to create some sort of
training journal, with reviewed training papers.
